\documentclass[10pt]{article}
\title{My use case Project}
\begin{document}
\maketitle
\tableofcontents

\section{Team: The Shield}
\begin{enumerate}
\item Kirandeep Kaur: C0741453
\item Lovepreet Kaur: C0747018
\item Jasvir Singh Laddi: C0748659
\item Amitdeep Brar: C0754202
\item Divyansh Bahubal: C0747855
\end{enumerate}

\section{USE Case 1: The Statement Of Work}
\subsection{Goal}
A SOW is primarily there to show our project stakeholders about our methodology and requirements.
\subsection{Actors}
Project Manager and the Team members who will document the Project.
\subsection{Scenario}
\begin{enumerate}
\item Users can directly access to the Web Application via URL.
\item The user will then be required to register to our software.
\item Then, the User will get his username and password.(to log in to the page)
\item The user can now access the software using that id.
\item The user will get the outline of our software after logging in.
\end{enumerate}

\section{USE Case 2: The Work Breakdown Structure}
\subsection{Goal}
To breakdown our project into smaller tasks so that it becomes easier to manage it and work on it.
\subsection{Actors}
Project Manager
\subsection{Scenario}
\begin{enumerate}
\item The leader needs to break down his work into smaller tasks.
\item Then he can assign tasks to all the members of the team.
\item The team members then analyze and design the project as per the requirements.
\item Finally, they come up with different ideas that leads them to execute the project.
\end{enumerate}

\section{USE Case 3: Creating the Resource Register}
\subsection{Goal}
 To make our project actually serve the audience.
\subsection{Actors}
Project Manager 
\subsection{Scenario}

\begin{enumerate}
\item The Project Manager has to submit the project to the authority to publish it on internet.
\item Then the authority will check it out and make the decision about it.
\item After getting a permision from the authority we can make it visible on internet to get access on it.

\end{enumerate}

\end{document}